Eco-evolutionary dynamics of finite populations from first principles

### 2023-02-09 ind_files/03_BD_processes.tex
Add footnote justifying b-d functional forms

In this multi-dimensional case, the macroscopic description amounts to a description of evolutionary game theory under mild assumptions on the birth and death rate vectors. We show this below, using methods first outlined by \citep{page_unifying_2002}. Let us assume that we can write the birth and death rate vectors as

@@

b^{(K)}_i(\mathbf{x}) &= \mu Q_i(\mathbf{x}) + x_ib^{\textrm{(ind)}}_{i}(\mathbf{x})\\

@@

where $\mu \geq 0$ is a constant describing the mutation rate, $Q_i(\mathbf{x})$ is a real-valued function that describes the birth rate of type $i$ individuals due to mutations in the population $\mathbf{x}$, and $b^{\textrm{(ind)}}_{i}(\mathbf{x})$ and $d^{\textrm{(ind)}}_{i}(\mathbf{x})$ are real-valued functions that respectively describe the per-capita birth and death rate of type $i$ individuals. Our assumptions of the functional forms \eqref{nD_functional_forms_for_replicator} thus amount to saying that birth and death rates can be separated into mutational and non-mutational components, and furthermore that the density dependence of the birth and death rates due to non-mutational effects is in a form that allows us to write down per-capita birth and death rates. Plugging these definitions into \eqref{nD_det_limit} and writing it down component-wise, we obtain the equation

>>>>

In this multi-dimensional case, the macroscopic description amounts to a description of evolutionary game theory under mild assumptions on the birth and death rate vectors. We show this below, using methods first outlined by \citep{page_unifying_2002}. Let us assume that the birth and death rate functions have the functional form

@@

b^{(K)}_i(\mathbf{x}) &= x_ib^{\textrm{(ind)}}_{i}(\mathbf{x}) + \mu Q_i(\mathbf{x})\\

@@

where $b^{\textrm{(ind)}}_{i}(\mathbf{x})$ and $d^{\textrm{(ind)}}_{i}(\mathbf{x})$ are non-negative functions that respectively describe the per-capita birth and death rate of type $i$ individuals, $\mu \geq 0$ is a constant describing the mutation rate in the population, and $Q_i(\mathbf{x})$ is a non-negative function that describes the additional birth rate of type $i$ individuals due to mutations in the population $\mathbf{x}$ that cannot be captured in the per-capita birth rate\footnote{When $x_i = 0$, \emph{i.e.} there are no type $i$ individuals in the population, individuals of type $i$ may still be born through mutations during births of the other types. This cannot be captured in $b^{\textrm{(ind)}}_{i}(\mathbf{x})$ because the term $x_ib^{\textrm{(ind)}}_{i}(\mathbf{x})$ vanishes when $x_i = 0$. Note that no analogous problem exists for the death rate, since the death rate of type $i$ individuals must be 0 when $x_i$ is 0 to ensure that we never have negative population densities.}. Our assumptions of the functional forms \eqref{nD_functional_forms_for_replicator} thus amount to saying that birth and death rates can be separated into mutational and non-mutational components, and furthermore that the density dependence of the birth and death rates due to non-mutational effects is in a form that allows us to write down per-capita birth and death rates for each type. Plugging these definitions into \eqref{nD_det_limit} and writing it down component-wise, we obtain the equation
